---
title: "Financial Data Analytics Project"
author: "[Your Name]"
date: today
format:
  html:
    code-fold: true
    code-tools: true
    toc: true
    toc-depth: 3
    number-sections: true
bibliography: references.bib
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
#| label: load-packages
#| include: false

# Load required packages
library(tsfe)
library(tidyverse)
library(tidyquant)
library(fpp2)
library(forecast)
library(rugarch)
library(vars)

# Set default theme for ggplot2
theme_set(theme_minimal())
```

# Introduction

## Research Questions

[State your three research questions here - one from each section of the assignment]

1. Exploratory Analysis Question: [Your question here]
2. Time Series Modeling Question: [Your question here]
3. Advanced Analysis Question: [Your question here]

## Background

[Provide background information relevant to your research questions]

## Literature Review

[Brief review of relevant literature - remember to cite sources using @citation-key]

# Data and Methods

## Data Description

```{r load-data}
#| label: data-loading

# Example: Loading Russell 2000 data
data("indice")
russell <- indice$russell2000

# Convert to time series object if needed
russell_ts <- ts(russell, frequency = 252)  # 252 trading days per year

# Display first few rows
head(russell)
```

## Data Preparation

```{r data-prep}
#| label: data-preparation

# Calculate returns
russell_returns <- diff(log(russell)) * 100

# Basic summary statistics
summary(russell_returns)
```

## Methodology

### Exploratory Analysis Methods

[Describe methods for your exploratory analysis]

```{r exploratory}
#| label: exploratory-analysis

# Example: Create time series plot
ggplot(data = data.frame(Date = index(russell), Price = coredata(russell))) +
  geom_line(aes(x = Date, y = Price)) +
  labs(title = "Russell 2000 Index Over Time",
       x = "Date",
       y = "Price") +
  theme_minimal()

# Example: QQ plot for returns
qqnorm(russell_returns)
qqline(russell_returns)
```

### Time Series Modeling Methods

[Describe your modeling approach]

```{r modeling}
#| label: time-series-modeling

# Example: Fit ARIMA model
fit_arima <- auto.arima(russell_returns)
summary(fit_arima)

# Example: Model diagnostics
checkresiduals(fit_arima)
```

### Advanced Analysis Methods

[Describe your advanced analysis methods]

```{r advanced}
#| label: advanced-analysis

# Example: GARCH modeling
spec <- ugarchspec(variance.model = list(model = "sGARCH"),
                  mean.model = list(armaOrder = c(1,1)))
fit_garch <- ugarchfit(spec, russell_returns)
show(fit_garch)
```

# Results

## Exploratory Analysis Results

[Present and interpret your exploratory analysis findings]

```{r exploratory-results}
#| label: exploratory-results

# Add your exploratory analysis results and visualizations here
```

## Time Series Modeling Results

[Present and interpret your modeling results]

```{r modeling-results}
#| label: modeling-results

# Add your modeling results here
```

## Advanced Analysis Results

[Present and interpret your advanced analysis results]

```{r advanced-results}
#| label: advanced-results

# Add your advanced analysis results here
```

# Discussion

## Integration of Findings

[Discuss how the findings from your three analyses connect and complement each other]

## Practical Implications

[Discuss the practical implications of your findings]

## Limitations

[Discuss limitations of your analysis]

## Future Research

[Suggest directions for future research]

# References {.unnumbered}

::: {#refs}
:::

# Appendix {.unnumbered}

## AI Usage Statement

[Describe any AI tools used in this analysis and how they were used]

## Additional Analyses

[Any additional analyses or robustness checks]

```{r appendix}
#| label: appendix-analyses

# Additional analyses can go here
```

## References Explained

### Section 1: Exploratory Analysis

- Q1 (Stock market behavior): Cont (2001) on empirical properties of returns
- Q2 (Earnings patterns): Foster (1984) on quarterly earnings analysis
- Q3 (Exchange rate volatility): Andersen et al. (2001) on volatility distributions

Section 2: Time Series Modeling

- Q1 (ARIMA prediction): Box et al. (2015) on time series analysis
- Q2 (Smoothing techniques): Cleveland et al. (1990) on decomposition
- Q3 (GARCH modeling): Bollerslev (1986) on GARCH models

Section 3: Advanced Analysis

- Q1 (Market connections): Forbes & Rigobon (2002) on market interdependence
- Q2 (Machine learning): Gu et al. (2020) on ML in finance
- Q3 (VAR models): Sims (1980) on VAR analysis


# References

Section 1: Exploratory Analysis References
1.	Cont, R. (2001). “Empirical properties of asset returns: stylized facts and statistical issues.” Quantitative Finance, 1, 223–236.
•	URL: https://www.tandfonline.com/doi/abs/10.1080/713665670
2.	Foster, G. (1984). “Quarterly accounting data: Time-series properties and predictive-ability results.” Accounting Review, 59(1), 1–21.
•	URL: https://www.jstor.org/stable/246028
3.	Andersen, T. G., Bollerslev, T., Diebold, F. X., & Labys, P. (2001). “The distribution of realized exchange rate volatility.” Journal of the American Statistical Association, 96(453), 42–55.
•	URL: https://www.tandfonline.com/doi/abs/10.1198/016214501750332965

Section 2: Time Series Modeling References

4.	Box, G. E. P., Jenkins, G. M., Reinsel, G. C., & Ljung, G. M. (2015). “Time series analysis: forecasting and control.” Journal of Business & Economic Statistics.
•	URL: https://www.wiley.com/en-se/Time+Series+Analysis%3A+Forecasting+and+Control%2C+5th+Edition-p-9781118675021
5.	Cleveland, R. B., Cleveland, W. S., McRae, J. E., & Terpenning, I. (1990). “STL: A seasonal-trend decomposition procedure based on loess.” Journal of Official Statistics, 6(1), 3–73.
•	URL: https://www.wessa.net/download/stl.pdf
6.	Bollerslev, T. (1986). “Generalized autoregressive conditional heteroskedasticity.” Journal of Econometrics, 31(3), 307–327.
•	URL: https://public.econ.duke.edu/~boller/Published_Papers/joe_86.pdf

Section 3: Advanced Analysis References

7.	Forbes, K. J., & Rigobon, R. (2002). “No contagion, only interdependence: measuring stock market comovements.” The Journal of Finance, 57(5), 2223–2261.
•	URL: https://onlinelibrary.wiley.com/doi/abs/10.1111/0022-1082.00494
8.	Gu, S., Kelly, B., & Xiu, D. (2020). “Empirical asset pricing via machine learning.” The Review of Financial Studies, 33(5), 2223–2273.
•	URL: https://academic.oup.com/rfs/article/33/5/2223/5542000
9.	Sims, C. A. (1980). “Macroeconomics and reality.” Econometrica, 48(1), 1–48.
•	URL: https://www.jstor.org/stable/1912017